### 2014-09-05 generic.Rmd
Factoring out the residuals computation.
@petrelharp -- this works great for the command line RScript, but when I try to
have it do a thing in the RMarkdown world, I get this error:

```
Quitting from lines 37-38 (generic.Rmd)
Error in ifelse(ds == 0, 1, Ne * expm1(-2 * ds)/expm1(-2 * Ne * ds)) :
  argument "Ne" is missing, with no default
Calls: render ... predictcounts.context -> predictcounts -> update -> <Anonymous> -> ifelse
```

please help!

## Invocation

```{r}
cat(model@invocation)
```

@@

```{r}
counts <- model@counts@counts
head(counts) # for some reason the code doesn't work if we don't print out some of the counts
cat("left window size:", model@counts@leftwin,
    "\ntotal window size:", nchar(rownames(counts)[[1]]))
cat("total counts:", sum(counts))
```

@@

## residuals for sufficiently short T-mers you can look at all of them (2-2? 3-1?)
## the top and bottom residuals for longer T-mers (9-5? 9-9?)
## if present, MCMC traces
## ... and posterior marginal distributions.

>>>>

```{r}
source("context-inference-fns.R")
cat(model@invocation)
```

@@

```{r}
counts <- model@counts@counts
head(counts) # for some reason the code doesn't work if we don't print out some of the counts
cat("left window size:", model@counts@leftwin,
    "\ncomplete window size:", nchar(rownames(counts)[[1]]),
    "\ntotal counts:", sum(counts))
```

@@

## residuals for sufficiently short T-mers you can look at all of them (2-2? 3-1?)

```{r}
computeresids(model)
```

## the top and bottom residuals for longer T-mers (9-5? 9-9?)
## if present, MCMC traces
## ... and posterior marginal distributions.
